---
title: "Dextromethorphan qualification report" # Title of the document
subtitle: "" # Subtitle of the document. May be left empty
author: "esqLABS GmbH"
date: "now"
date-format: "YYYY-MM-DD HH:mm:ss"
params:
  # If `TRUE`, results will be loaded
  # Sub-folder where simulated results is located, in case `loadPreSimulatedResults`
  # is `TRUE`. If `NULL`, default results folder as specified in `ProjectConfiguration`
  # is used.
  # Sub-folder where the results will be stored. If NULL, a folder in the "Results"
  # folder with current data name will be created.
  # If TRUE, parameters defined in "InputCode/TestParameters.R" will be applied to all
  # simulations
  # If set to TRUE, only static content of the report will be generated,
  # i.e., R code will not be executed
  loadPreSimulatedResults: TRUE
  loadResultsFolder: "2023-07-21 12-59"
  saveResultsFolder: NULL
  setTestParameters: FALSE
  createOnlyStaticContent: FALSE
output-file: "Dextramethorphan qualification report"
format:
  pdf: 
    # table of contents and lists
    # Caption locations
    # Other
    # Figures rendering
    # Document layout as used by Word reports
    toc: true # display table of content (TOC)
    toc-depth: 3 # display three levels in TOC
    toc-title: Table of Content # override default "Content" TOC title
    lof: false # Print list of figures?
    lot: false # Print list of tables?
    fig-cap-location: bottom # figure captions location
    tbl-cap-location: bottom # table captions location
    number-sections: true # add number to sections
    colorlinks: true # links format
    fig-pos: "H" # ensure plots don't move to bottom of doc
    fig-align: center # plots are centered by default
    geometry:
      - top=25.4mm
      - bottom=25.4mm
      - left=25.4mm
      - right=25.4mm
    papersize: A4
   # fontfamily: "Segoe UI" # Can we use "Segoe UI Light" here?
execute:
  echo: false # do not show code chunks
  output: true
  warning: false # do not print warning
  cache: false # do not use cache unless specified in chunks
link-citations: TRUE
reference-section-title: "References"
editor:
  markdown:
    wrap: 72
editor_options:
  chunk_output_type: console
bibliography: references.bib
---

```{r setup, message=FALSE, include = FALSE, eval = !params$createOnlyStaticContent}
wd <- file.path(getwd(), "..")
setwd(wd)
source("Report/utilities-report/initEsqlabsProject.R")
projectConfiguration <- initEsqlabsProject()
```

```{r runSimulations, eval=!params$createOnlyStaticContent}
setwd(wd)
projectConfiguration$scenarioDefinitionFile <- "Scenarios_dextro.xlsx"
scenarioNames <- NULL
scenarioResults <- simulateScenarios(
  projectConfiguration = projectConfiguration,
  loadPreSimulatedResults = params$loadPreSimulatedResults,
  setTestParameters = params$setTestParameters,
  scenarioNames = scenarioNames,
  loadResultsFolder = params$loadResultsFolder,
  saveResultsFolder = params$saveResultsFolder
)
```

```{r loadData, message=FALSE, include = FALSE, eval = !params$createOnlyStaticContent}
setwd(wd)
# Load from PKML
projectConfiguration$dataFolder <- "Data/Dextromethorphan"
observedData <- esqlabsR::loadObservedDataFromPKML(projectConfiguration)

# # Or load from excel
# dataSheets <- c("Sheet 1")
# 
# observedData <- esqlabsR::loadObservedData(
#   projectConfiguration = projectConfiguration,
#   sheets = dataSheets
# )
```

```{r createPlots, eval = !params$createOnlyStaticContent}
setwd(wd)
plotGridNames <- NULL
allPlots <- createPlotsFromExcel(
  simulatedScenarios = scenarioResults$simulatedScenarios,
  observedData = observedData,
  projectConfiguration = projectConfiguration,
  plotGridNames = plotGridNames
)
```

```{r exportPlots, eval = !params$createOnlyStaticContent}
# Export plots to png
#Create export configuration that will be used for exporting plots.
exportConfiguration <- createEsqlabsExportConfiguration(projectConfiguration)
# Figures should be saved in the same folder as the location of the report
# plus subfolder "Figures"
exportConfiguration$path <- file.path(getwd(), "Figures")
# Export each created plot
for (plotName in names(allPlots)){
  plot <- allPlots[[plotName]]
  # Replace "\" and "/" by "_" so the file name does not result in folders
      plotName <- gsub(pattern = "\\", "_", plotName, fixed = TRUE)
      plotName <- gsub(pattern = "/", "_", plotName, fixed = TRUE)
      exportConfiguration$name <- plotName
      # Save plot
      exportConfiguration$savePlot(plot)
}
```

\newpage

::: callout-note
```{r resultsOrigin, echo=FALSE, results='asis'}
if (params$loadPreSimulatedResults) {
  cat(
    "This report has been created with simulation results loaded from results folder ",
    params$loadResultsFolder, ".\n"
  )
} else {
  cat("This report has been created by running the simulations.")
}

if (params$setTestParameters) {
  cat("WARNING: `setTestParameters` is set to `TRUE`!")
}
```
:::

\newpage

# Introduction

This document describes the qualification of a published
dextromethorphan physiologically-based pharmacokinetics (PBPK) model for
the use with the Open Systems Pharmacology Software (OSPS) Version 11.2.

The PBPK model has been developed with OSPS version 9.1 and published by
[@rüdesheim2022]. Model snapshots have been downloaded on 16.06.2023
from the Open Systems Pharmacology (OSP)
[repository](https://github.com/Open-Systems-Pharmacology/Dextromethorphan-Model).
As of 16.06.2023, no model version qualified for OSP version 11.2 is
publicly available.

# Methods

## Software

For recreating the original results from the publication, OSPS [version
9.1](https://github.com/Open-Systems-Pharmacology/PK-Sim/releases/tag/v9.1)
was used. The qualification is done with OSPS [version
11.2.142](https://github.com/Open-Systems-Pharmacology/PK-Sim/releases/tag/v11.2.142).

## Drug-gene-interaction

The model is intended to be used in drug-drug interactions (DDI)
simulations with dextromethorphan as a CYP2D6 victim. Drug-gene
interactions (DGI) to describe variabilities of CYP2D6 activity are
modeled as variations of the catalytic rate constant $k_{cat}$.
Following values are used in the project:

## Qualification process


## Consolidation of expression profiles


# Results

Comparison of time-concentration profiles generated with the different
software versions are presented in the following:

```{r printFigures, results = 'asis', eval = TRUE}
if (params$createOnlyStaticContent) {
  fileNames <- list.files(path = file.path(getwd(), "Figures"),
                          pattern = "*.PNG",
                          full.names = FALSE)
  plotNames <- tools::file_path_sans_ext(fileNames)
} else {
  plotNames <- sort(names(allPlots))
}

for (plotName in plotNames){
  plotName <- gsub(pattern = "\\", "_", plotName, fixed = TRUE)
  plotName <- gsub(pattern = "/", "_", plotName, fixed = TRUE)
  filePath <- file.path(getwd(), "Figures", paste0(plotName, ".png"))
  cat("![", plotName, "](", filePath,")\n")
}
```

# Conclusion

