---
title: "esqlabsR.report.template" # Title of the document
subtitle: ""
author: "esqLABS GmbH"
date: "now"
params:
  runMainScript: no
  projectConfigurationFile: "../../../ProjectConfiguration.xlsx" # relative path from this document
  saveResultsFolder: "data/"
  saveFiguresFolder: "figures/"
  loadPreSimulatedResults: no
  setTestParameters: true
  loadResultsFolder: no
---

\newpage


```{r message=FALSE, eval = params$runMainScript}
source("scripts/main.R")
main(params = params)
```


# Notes

::: {.callout-note}
```{r}
if (params$loadPreSimulatedResults) {
  cat(
    "This report has been created with simulation results loaded from results folder ",
    params$saveResultsFolder, ".\n"
  )
} else {
  cat("This report has been created by running the simulations.")
}
```
:::


```{r, results='asis'}
if (params$setTestParameters) {
cat(
"::: {.callout-warning}
`setTestParameters` is set to `TRUE` !
:::"
)}
```

\newpage

# Introduction

{{< include texts/introduction.md >}}


# Methods

## Software

The qualification is performed with OSPS [version
11.2.142](https://github.com/Open-Systems-Pharmacology/PK-Sim/releases/tag/v11.2.142).

## Qualification process

1.  Import project snapshot "paroxetine-model.json" in PK-Sim v11.2.

2.  The snapshot contains 33 simulations. All simulations were exported
    to `*.pkml` for simulation in R.

3.  All observed data from the project created with version 11.2 were
    exported `*.pkml` for loading in R.

4.  Simulations were simulated in R and the results visually compared to
    the results reported in the original publication.
    
## Data

## Model consolidation

During conversion of projects created with versions before 11, a
separate expression profile is created for each individual. To ensure
that all individuals are using the same expression, expression profiles
of the same protein were compared. All expression profiles for the same
protein were equal. Therefore, the same expression profile was set in
every individual, and the remaining profiles were removed.

# Results

Comparison of time-concentration profiles with observed data are
presented in the following:

```{r}
# list files we want to display
figs <- list.files("figures/", pattern = "\\.[pj][pn]g", full.names = TRUE)
# Extract the name of the plot from the files names
figs_names <- fs::path_ext_remove(fs::path_file(figs))
```


```{r}
#| fig-cap: !expr figs_names
knitr::include_graphics(figs)
```

# Conclusion

All simulations that are available in the snapshot produced the same results 
as in the original publication (by visual comparison). Not all reported simulations
are implemented in the snapshot, their comparison was not possible. It is, however,
assumed that the model behaves exactly as described in the original publication.


